The Array of Long-Baseline Antennas for Taking Radio Observations from the Sub-Antarctic

### 2020-05-12 albatros_paper.tex
minor edits before merging some stuff from Cynthia

A bank of four parallel \SI{12}{V}, \SI{200}{\ampere\hour} batteries serves to power to the two-element pathfinder sysytem. A Honda EU30is generator is run periodically to charge the battery bank, which can run the system for approximately four days on a full charge.  DC/DC converters power the SNAP board, the FEE, the amplifiers and the clock.
% Cuts (redundant or too much detail)
% and the fuel is kept in one of the shipping containers at the \prizm\ site
% The power from the battery bank is connected to the Faraday cage where the power regulation is performed.
\subsection{Software and data acquisition}
\attention{Nivek?} \\
Text goes here.

@@

\subsection{Solar power system}
\attention{Nivek, Tankiso, Eamon?} \\
The power system of the ALBATROS-EGG uses generators to charge the batteries manually every once in a number of days. From the observation that has been made, the batteries take $\approx$ 2 days to discharge to a point where the system shuts down. Because of the weather conditions in Marion Island, an individual can sometimes be unable to go to the site to charge the batteries, which means that if the weather does not allow, the system can be shut down for a long period. Thus, a solar power system solution was introduced to the ALBATROS so that the system can continously run without having to be recharged manually and often.\\

>>>>

A bank of four parallel \SI{12}{V}, \SI{200}{\ampere\hour} batteries serves to power the two-element pathfinder system. A Honda EU30is generator is run periodically to charge the battery bank, which can run the system for approximately four days on a full charge.  DC/DC converters power the SNAP board, the FEE, the amplifiers and the clock.
% Cuts (redundant or too much detail)
% and the fuel is kept in one of the shipping containers at the \prizm\ site
% The power from the battery bank is connected to the Faraday cage where the power regulation is performed.
\subsection{Software and data acquisition}
\attention{Nivek?} \\
Text goes here.

@@

\subsection{Solar power system}
\attention{Nivek, Tankiso, Eamon?} \\
Although the first-deployed two-element pathfinder setup uses generators to periodically recharge batteries, the bulk of the antenna stations that will comprise the full array will be located at points farther removed from the main base, and will require a fully autonomous energy source.

The power system of the ALBATROS-EGG uses generators to charge the batteries manually every once in a number of days. From the observation that has been made, the batteries take $\approx$ 2 days to discharge to a point where the system shuts down. Because of the weather conditions in Marion Island, an individual can sometimes be unable to go to the site to charge the batteries, which means that if the weather does not allow, the system can be shut down for a long period. Thus, a solar power system solution was introduced to the ALBATROS so that the system can continously run without having to be recharged manually and often.\\
